---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/readme/README-"
)
```

# `ghql`

Using a quick query language to pull multiple api requests at once.

  * [installation](#install-ghql)
  * [tidy function](#tidy-issues)
  * [using with github](#working-with-github)

## Install ghql

```{r install, eval = FALSE}

remotes::install_github("ropensci/ghql")

```

```{r}
library(magrittr)
```

## Query Objects

open a new query object

```{r remedy001}

qry <- ghql::Query$new()

```

define the grapql query

```{r remedy002}

qry$query('user_states','{
          viewer {
    repositories(privacy:PUBLIC,first: 30) {
      pageInfo {
        hasNextPage
        endCursor
      }
      edges {
        node {
          name
          pullRequests(states:[OPEN],last: 20, orderBy: {field: CREATED_AT, direction: DESC}) {
      		edges {
            node {
              title
              number
              state
              createdAt
              author{
                login
              }
            	}
      			}
    			}
          issues(states:[OPEN],last: 20, orderBy: {field: CREATED_AT, direction: DESC}) {
      		edges {
            node {
              title
              number
              state
              createdAt
              author{
                login
              }
            	}
      			}
    			}
        }
      }
    }
  }
}')

```

## tidy issues

```{r remedy003}

tidy_issues <- function(x){
  
  x1 <- jsonlite::fromJSON(x)
  
  edges <- purrr::transpose(x1$data$viewer$repositories$edges)%>%
    dplyr::as_tibble()
  
  open_edges <- edges%>%
    dplyr::select(name,pullRequests)%>%
    tidyr::unnest()%>%
    dplyr::rename(open_pullRequests = edges)%>%
    dplyr::left_join(
      edges%>%
        dplyr::select(name,issues)%>%
        tidyr::unnest()%>%
        dplyr::rename(open_issues = edges),
      by='name'
    )
 
  PR <- purrr::transpose(open_edges$open_pullRequests)%>%
    purrr::flatten()%>%
    purrr::set_names(open_edges$name)%>%
    purrr::discard(.p = is.null)%>%
    purrr::map_df(.f=function(x) {
      x$author <- purrr::flatten_chr(x$author)
      x},.id = 'repository')%>%
    dplyr::mutate(type = 'pull_request')%>%
    dplyr::select(-state)
  
  ISSUES <- purrr::transpose(open_edges$open_issues)%>%
    purrr::flatten()%>%
    purrr::set_names(open_edges$name)%>%
    purrr::discard(.p = is.null)%>%
    purrr::map_df(.f=function(x) {
      x$author <- purrr::flatten_chr(x$author)
      x},.id = 'repository')%>%
    dplyr::mutate(type = 'issue')%>%
    dplyr::select(-state)

  output <- dplyr::bind_rows(PR,ISSUES)
  
  output$createdAt = as.POSIXct(output$createdAt, "UTC", "%Y-%m-%dT%H:%M:%S")
  output$days_passed = as.numeric(difftime(Sys.time(),output$createdAt,units = 'days'))
  
  output
  
}

```

## Working with Github

load gh client with GITHUB_PAT

```{r remedy004}
  
    cli_gh <- ghql::GraphqlClient$new(
      url = "https://api.github.com/graphql",
      headers = httr::add_headers(Authorization = sprintf("Bearer %s", Sys.getenv("GITHUB_PAT")))
    )

```

load the schema

```{r remedy005}
  
cli_gh$load_schema()

```

execute the graphql query

```{r remedy006}
  
x_gh <- cli_gh$exec(qry$queries$user_states)       

```

tidy up

```{r remedy007}
  
output <- tidy_issues(x_gh)

```

```{r}
output%>%
  dplyr::glimpse()
```

<details>
<summary> <span title='Click to Expand'> Pull Request Table </span> </summary> 
 
```{r}
output%>%
  dplyr::filter(type=='pull_request')%>%
  knitr::kable()

```

</details>
 
<details>
<summary> <span title='Click to Expand'> Issues Table </span> </summary>
 
```{r}
output%>%
  dplyr::filter(type=='issue')%>%
  knitr::kable()

```

</details>